---
title: "W_UP_01"
author: "Daniela Olvera-Mota"
date: "fall 2023"
output: html_document
---



The report structure should include five sections.  see below



```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
mydata <- read.csv(file="pushups.csv")
```

# Introduction

<!--In this section you explain what you are trying to show. Where did the data come from? What is the research or other question you are trying to answer?!-->

Create an Rstudio project in your shared space on rstudio.cloud.  Using the dataset called pushups from the tigerstats package in R; answer the question posed by this null and alternate hypothesis in an html markdown document.

Is there a difference in the average number of push ups that can be done between the 2 positions ( line  vs skills) in 2 minutes ? 
The data came from george town in kentucky.

$H_0$: There is no difference between the average number of pushups of line vs skill players

$H_A$: The average number of pushups done by line players is statistically different than that of skill players. 

# Methods

<!--Decide on your methods: use "variable analysis" or other appropriate descriptors. Make sure to choose at least one graphical method and at least one numerical method.!-->
Push ups is a numerical variable, position is categorical.Therefore, we would use numerical-cat file.

# Results

<!--Divide this section into two sub-sections: One for your descriptive results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here. Make sure to show your code. Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too. Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->
```{r}
boxplot(pushups~position,data=mydata)
```

The plot shows that the line players did on average roughly about 17 pushups in 2 minutes and the skills players did roughly about 49 pushups in 2 minutes.It shows skills players did more pushups than line players in 2 minutes.

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
favstats(pushups~position,data=mydata)
```
The table shows that the skills players did 3x more than the line players did in pushups. The average pushups for a line player was 17 and for skill it was 49.

## Inferential Results
```{r}
t.test(pushups~position,data=mydata)
```

<!--State hypothesis clearly. Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc. Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->


# Discussion and Conclusion

<!--Discussion and conclusion here. If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason. Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

The original question was , is there a difference in the average number of push ups that skill and line players can do in 2 minutes? Since the p value, which is 0.00000942, is so small we know that the null hypothesis is not correct.The p value is less than 0.5 so we know to reject the null hypothesis (which was that there's no difference in the average number of push ups between the two teams). We conclude that there is a difference in the average number of pushups between the two teams. 